\begin{abstract}
\par The Purpose of Training and Placement Portal is to automate the existing manual system by the help of computerized equipment’s and full-ﬂedged computer software, fulﬁlling their requirements, so that their valuable data can be stored for a longer period of time with easy accessing. 
\\
\par Also,manipulation of the data becomes simpler. The required software and hardware are easily available and easily accessible to work hands-on. Training and Placement Portal, as described above can lead to error free, secure, reliable and fast management system. It can assist the TPO to concentrate on their activities rather than concentrating on record keeping. Thus, it will help our college in better utilization of time and human resources. TPO can maintain computerized records without redundant entries. 
\\
\par These current existing system is not computerized. All transactions in the system are done manually such as maintaining records. To make this tedious job simple, the we have to computerize the system. The management that have been carrying out this job manually makes the job more complicated and tedious most of the times. For example, in the earlier system TPO has to collect student details for placements. Approving those student details takes lot of time. TPO and students have to consult each other directly if any information is required. This system reduces the manual work and requires less paper work which basically improves time efficiency. This project is developed with PHP for front-end and MY SQL for back-end. 
\end{abstract}
