\chapter{Introduction}

\par The Placement Cell plays a crucial role in locating job opportunities for Under Graduates and Post Graduates passing out from the college by keeping in touch with reputed firms and industrial establishments. The Placement Cell operates round the year to facilitate contacts between companies and graduates
\\

\section{Description}
\hspace{5mm} In today’s world everyone is striving for jobs after completion of their graduation. It is necessary for each and every student, but for that they need to take efforts in search of desired jobs. For simplicity of this whole hectic procedures, we propose \textbf{Training and Placement Portal} because the current system is totally manual, time consuming and makes it very difficult to maintain coordination between student, TPO and companies. \\

This portal is developed to maintain the details of student's information, the information about the company availability. Through this portal, the student may know all the details of the events which will be provided by the TPO, the student can view the information of the upcoming company and dates of the upcoming drives.\\ 

The placement cell adds the companies to select their students for jobs via the campus interview. It allows the companies to view the student’s resumes in a selective manner. They can filter the student’s profile as per their requirement. The job details of the placed students will be provided by the administrator. The administrator plays an important role in our project. Our project provides the facility of maintaining the details of the students and gets the requested list of candidates for the company who would like to recruit the students based on given query.
\pagebreak

\section{Objective}
 \par The TPO cell arranges training programmes like Aptitude, Mock Interviews, Group Discussions, Communication Skills Workshop etc and it also organizes Public Sector Exam Training for students who are interested to join Government Sectors. It also invites HR Managers from different industries to conduct training programmes for final year students.\\
 
\par The students are trained to attain placement through a variety of programmes run by the Training and Placement cell such as:

\begin{itemize}
\item Industry to Institute Programmes – Corporate leaders from leading industries are invited regularly to interact with students.
\item Various Training Programmes are organized to train the students in the areas of Aptitude, Quantitative Reasoning, Logical Reasoning and Verbal through the Reputed External Training centers and IIM Alumni's.
\item Technical training programmes are being conducted by Technical experts.
\item Training through Mock Interviews for students to perform well in the professional interviews as per the expectations of the corporate world.
\item Public Sector Exams Training.
\end{itemize}






\pagebreak

\section{Existing System}
\subsubsection{Pitfalls of Existing Systems}
\pagebreak
\section{Proposed System}
\subsubsection{Admin (Training and Placement Officer)}
\subsubsection{TPO Co-Ordinator}
\subsubsection{Student}
\subsubsection{HOD}



